### 2020-10-16 doc/manuscript/Dow_manuscript.Rmd
worked on results

*Climate windows*

•	Climwin results (Figs. `r climwin`, `r climwin_rp_DOY25_SCBI`, `r climwin_dp_DOY25_SCBI`)

>>>>

*Optimal climate windows*

For the majority of weekly time windows from Feb. 1 to $DOY_{25}$, there was negative relationship between temperature and $DOY_{25}$, meaning that warmer temperatures shifted growth earlier in the season (Figs. `r climwin`, `r climwin_rp_DOY25_SCBI`, `r climwin_dp_DOY25_SCBI`). 
This held true for both ring- and diffuse-porous trees, *albeit* with stronger relationships for ring-porous trees. 
*(Describe the landscape:)*
In general, there were significant negative relationships between temperature and $DOY_{25}$ for any time period beginning $\ge$ **5** weeks prior to $DOY_{25}$, ending  $\le$ **6** weeks prior, and covering at least a **3**-week period. 
Relationships tended to be weaker and more stochastic in sign for short time periods, particularly those just prior to $DOY_{25}$.

Optimal windows occurred from **##-##** for ring-porous species and from **##-##** for diffuse-porous species.
